\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-10-03 paper/tables/tabBoilerplateIllustration.tex
updated table 4; now shows the 20 most frequent lines, sorted according to their boilerplate probability

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Sat Jul 28 20:51:59 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Substantive & Boilerplate \\ 
  \hline
have questions & 0.00 & 1.00 \\ 
  stay connected & 0.00 & 1.00 \\ 
  accident or injury & 0.00 & 1.00 \\ 
  fire damaged buildings & 0.00 & 1.00 \\ 
  gas connections & 0.00 & 1.00 \\ 
  harboring of vagrants & 0.00 & 1.00 \\ 
  roof system problem & 0.00 & 1.00 \\ 
  violation plat note & 0.00 & 1.00 \\ 
  violation setback & 0.00 & 1.00 \\ 
  violation site plan & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
\end{table}

>>>>

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Oct  2 23:59:06 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Boilerplate Probability & Line Frequency \\ 
  \hline
elections & 0.92 & 4895 \\ 
  assembly & 0.91 & 6996 \\ 
  library & 0.91 & 4888 \\ 
  ombudsman & 0.90 & 2930 \\ 
  of & 0.90 & 2767 \\ 
  police department & 0.90 & 5101 \\ 
  office & 0.90 & 2926 \\ 
  fire department & 0.90 & 5047 \\ 
  municipal clerk & 0.89 & 3440 \\ 
  parks and recreation & 0.89 & 5397 \\ 
  assembly memorandum no & 0.89 & 4827 \\ 
  boards and commissions & 0.89 & 3012 \\ 
  municipality of anchorage & 0.89 & 3357 \\ 
   & 0.88 & 461487 \\ 
  anchorage alaska page & 0.88 & 5684 \\ 
  resolution no ar & 0.88 & 4627 \\ 
  a assembly memorandum no & 0.86 & 4579 \\ 
  health and human services & 0.84 & 2863 \\ 
  regular assembly meeting page & 0.81 & 3080 \\ 
  economic and community development & 0.74 & 2891 \\ 
   \hline
\end{tabular}
\endgroup
\caption{The 20 most frequent lines in the corpus of Anchorage, AK, sorted according to the probability with which the classifier identifies them as boilerplate. This table illustrates that the boilerplate classifier correctly flags and removes interpretable but unimportant content which would otherwise have a disproportionate impact on the topic model.} 
\label{tabBoilerplateIllustration}
\end{table}
